What Does Reproducible Research Mean for Plant Pathology?

### 2017-04-19 README.rmd
Convert project to R package

---
title: "What Does Reproducible Research Mean for Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.  Adam H. Sparks: Centre for Crop Health, University of Southern Queensland, Toowoomba, Qld 4350, Australia
2.  Emerson M. Del Ponte: Universidade Federal de Viçosa, Viçosa, MG, Brasil
3.  Niklaus J. Grünwald: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA
4.  Zachary Foster: Horticultural Crops Research Laboratory, USDA Agricultural Research Service, Corvallis, OR 97330, USA

ABSTRACT
========

Once complete the abstract will be here.

Full text
=========

The full text of the document can be found here in a [MS Word file](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/blob/master/What_Does_Reproducible_Research_Mean_for_Plant_Pathology.docx) compiled from this [R Markdown document](https://github.com/adamhsparks/Reproducible-Research-in-Plant-Pathology/blob/master/What%20Does%20Reproducible%20Research%20Mean%20for%20Plant%20Pathology.Rmd).

>>>>

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Links to various resources that are useful for this document

[Replication data collection highlights value in diversity of replication attempts](http://www.nature.com/articles/sdata201728)

[The reproducibility crisis in science and prospects for R](https://www.r-statistics.com/2016/07/the-reproducibility-crisis-in-science-and-prospects-for-r/)

[rrrpkg - Use of an R package to facilitate reproducible research](https://github.com/ropensci/rrrpkg)

### 2017-04-19 inst/paper/What Does Reproducible Research Mean for Plant Pathology.Rmd
Convert project to R package

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
* Example from my lab: 
  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
* Other examples from plant pathology providing e-Xtras or supplemental material

>>>>

## WHAT IS THE STATE OF REPRODUCIBLE RESEARCH IN PLANT PATHOLOGY?
* Madden et al. [-@Madden2015] supply an *e-**X**tra*\* with repoducible examples
for readers.
* Duku et al. [-@Duku2016] provide models, data and code, (http://adamhsparks.github.io/MICCORDEA/) necessary to
replicate the entire study modelling the effects of climate change on rice
bacterial blight and rice leaf blast in Tanzania.
* Sparks et al. [-@Sparks2011; -@Sparks2014] provide models, data and code, (http://adamhsparks.github.io/Global-Late-Blight-MetaModelling/)
necessary to replicate model development and the subsequent the study on the effects of climate change on potato late blight.
* Del Ponte provides data and a reproducible report that explan in details all steps of the analysis and the R codes for conducting a meta-analysis for assessing heterogeneity in relationship between white mold incidence and soybean yield and between incidence and soybean yied.
* Example from Grunwald lab: 
  - paper http://apsjournals.apsnet.org/doi/full/10.1094/PHYTO-12-14-0350-FI
  - github repo https://github.com/grunwaldlab/Sudden_Oak_Death_in_Oregon_Forests
* Other examples from plant pathology providing e-Xtras or supplemental material
